---
title: | 
  | Replication Material 
  | 
  | Coordination inside government administrations: Lessons from the EU Commission 
  |
  | doi: https://doi.org/10.1111/gove.12525
author: "Roman Senninger, Daniel Finke, and Jens Blom-Hansen"
date: "Contact: rsenninger@ps.au.dk"
output: 
  bookdown::html_document2:
    theme: cosmo
    highlight: kate
    toc: true
    number_sections: false
    toc_float:
     collapsed: false
     smooth_scroll: false
    code_folding: show
    fig_width: 5
    fig_height: 5 
---

```{r setup, include = F}
knitr::opts_knit$set(root.dir = '/Users/au506709/Dropbox/EUCORE/Papers/internal_coordination/replication_files/data/')
```

# Load Required Packages

```{r, eval = T, echo = T, include= T, message= FALSE}


library("visreg")
library("circlize")
library("gplots")
library("heatmaply")

```
 

# Content

This manual provides code to reproduce our results. We start with the results in Figure 1 showing a chord diagram of coordination relationships between DGs.

# Figure 1 

```{r, eval = T, echo = T, include=TRUE}


load("./chord.RData")

col_fun <- colorRamp2(range(chord$sum), c("gray90", "gray50"), transparency = 0.5)
grid.col = c("grey80")
par(cex = 0.7)
chordDiagram(chord, grid.col = grid.col, col = col_fun, directional = 1)


```


#Figure 2

```{r, eval = T, echo = T, include=TRUE}


load("./efcosine.RData")

heatmap.2(efcosine,  
          col = Greys,
          cexCol = 0.8,
          cexRow = 0.8,
          srtCol=45, 
          scale="none",
          margins=c(3,0), # ("margin.Y", "margin.X")
          trace='none', 
          symkey=FALSE, 
          symbreaks=FALSE, 
          dendrogram='none',
          density.info='histogram', 
          denscol="grey40",
          keysize=1, 
          #( "bottom.margin", "left.margin", "top.margin", "left.margin" )
          key.par=list(mar=c(4,0,3,0)),
          # lmat -- added 2 lattice sections (5 and 6) for padding
          lmat=rbind(c(5, 4, 2), c(6, 1, 3)), lhei=c(2.5, 5), lwid=c(1, 10, 1))


```


## Table 1   

Reproduce regression results in Table 1: 

```{r, eval = T, echo = T, include=TRUE}

load("./cisnet.RData")

model1 <- glm(coordination ~ cosine1 + spatial_lag + as.factor(year) + as.factor(DG), family = binomial(link = "logit"),  data = cisnet)

model2 <- glm(coordination ~ cosine1 * Salience + spatial_lag + as.factor(year) + as.factor(DG), family = binomial(link = "logit"),  data = cisnet)

```

# Figure 3 

```{r, eval = T, echo = T, include=TRUE}

# left panel 

visreg(model1, "cosine1", scale = "response", xlab="policy overlap", ylab = "P(coordination)", rug = 1, main = "", alpha = 0.01, 
       line=list(col="black", lwd=0.5),
       fill=list(col="gray80"), ylim=c(0, 1))


# right panel 

visreg(model2, "cosine1", by = "Salience", scale = "response", rug = 1, xlab = "policy overlap", ylab = "P(coordination)", overlay=T, 
       ylim=c(0, 1), line.par=list(col = c("black", "black"), lwd=0.5, lty = c("solid", "dashed")), fill.par=list(col=c("gray90", "gray70")))


```


# Additional Material 

The replication material includes the term frequency-inverse document frequency matrix as described on p. 11 of the article. 

```{r, eval = F, echo = T}

load("./tfidf.RData
```



